---
title: "P8105_HW1_cm3936"
author: "Carolyn Martinez"

date: "2024-09-16"
output: github_document 
---
```{r loading libraries}
library(ggplot2)
library(tibble)
library(tidyverse)
set.seed(123)
```
Problem 0.1 - Done 

Problem 0.2 - Done 

**Problem 1**

_**Description of "penguins" dataset:**_
```{r loading the data} 

penguins_data=data("penguins", package = "palmerpenguins")

```

```{r echo=FALSE}
mean_flipper =
    mean (penguins$flipper_length_mm, na.rm = TRUE, digits =2)

```
This data set has `r nrow(penguins)` observations and `r ncol(penguins)` variables which include the species of penguin, the island, length of the bill (in mm), depth of the bill (in mm), length of the flipper (in mm), body mass (in grams), sex, and year. 

The the data set has `r nrow(penguins)` rows and `r ncol(penguins)` columns. 

The mean flipper length is `r round(mean_flipper, digits= 2)` millimeters. 

_*Making the scatter plot*_

```{r flippervbill_scatter}
set.seed(123)
my_plot=ggplot(penguins, aes(x = bill_length_mm, y = flipper_length_mm, color=species)) + geom_point()

ggsave(filename="flippervbill.png", plot=my_plot)
```
**Problem 2**
The code chunk below creates the requested data frame with: 
- random sample of size 10 from a standard Normal distribution
- logical vector indicating whether elements of the sample are greater than 0
- character vector of length 10
- factor vector of length 10, with 3 different factor “levels”

```{r problem 2}
homework_df = tibble (
  norm_sample = rnorm(10),
  norm_sample_pos = norm_sample > 0,
  vec_char = length(10),
  vec_factor = factor(rep(c("level1", "level2", "level3"), length.out =10))
  
)
```

_*Taking the mean of the variables*_

The mean of all the variables are as follows: 

- mean of vec_char is `r mean(pull(homework_df, vec_char))`

- mean of vec_factor is `r mean(pull(homework_df, vec_factor))`

- mean of norm_sample is `r mean(pull(homework_df, norm_sample))`

- mean of norm_sample_pos is `r mean(pull(homework_df,norm_sample_pos))`

I notice that the mean of the factor variable is not being calculated because it is not "numeric or logical". The other variables do produce a mean. 


```{r applying the numeric function, eval=FALSE}
as.numeric(pull(homework_df,vec_char))
as.numeric(pull(homework_df,vec_factor))
as.numeric(pull(homework_df,norm_sample))
as.numeric(pull(homework_df,norm_sample_pos))

?as.numeric
```
When the `as.numeric` function is applied to the different variables I noticed that for vec_char all the values are the same (1), this is because all the values in the data frame are 1 due to the fact that I did not specify what the contents of it should be only that it be 10 items long. 


For vec_factor the values are 1, 2 or 3, this is because it only has three levels as established at the creation. 


In the norm_sample all the numbers are numeric, this is because the numbers were derived from a random sample.


In the norm_sample_pos variable the value is either 1 or 0, this i because the response to the variable is TRUE or FALSE, it is a binary variable therefore the only two numeric options are 0 or 1. 

This explains the values seen in the mean, it seems that when the mean is calculated, the variables are forcefully interpreted as numeric. 


